---
title: "HAR report"
author: "A. Zuoza"
date: "Friday, April 24, 2015"
output: html_document
---

```{r library, warning=FALSE, echo=FALSE, message=FALSE}
library(caret)
library(randomForest)
```

```{r loading_enviroment}
load(file = "./test2.RData")
load(file = "./test3.RData")
```

#Summary

This is the report of Practical Machine Learning course project.   
The data was downloaded from Coursera Course Web page. 
[Train data is here](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv) 
and [Test data is here](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv). <br>

The train data have `r dim(data.all)[1]` observations, one predictor (variable name 
classe) and `r dim(data.all)[2] - 1` regressors. <br>

The two models was build:   
 - model1 with 36 predictors;     
 - model2 with 40 predictors;
 
For model1, as predictors was choosen all gyrometer, accelerometer and magnetometer 
data for belt, arm, dumbbell and forearm on x, y and z axis's.    
On model2 I added tottal acceleration for belt, arm, dumebell and forearm.   

Both models was buid on 90% subset from original data set. I used Random Forest 
metode for models buiding.    
The accuracy on test data of model1 was `r round(model3$results[1, 2], digits = 3)` and 
accuracy of the model2 was `rround(model5$results[1, 2],digits = 3)`. The results of model2 
(with more predictors), was a little bit better as for model1. The predictions corss 
table is shown bellow:

```{r c_tab}
table(predict3, predict5)
```

In this table we can see, that most differences are in the prediction of "B" and 
"C" classes.

The model1 and model2 was tested with "real" test data (20 predictions for submission) showed, that 
it was only one difference between model1 and model2 predictions. The predictions 
corss table on "real" data is shown bellow:

```{r c_tab_final}
data.test.real <- read.csv("../pml-testing.csv")
predic.final3 <- predict(model3, data.test.real)
predic.final5 <- predict(model5, data.test.real)
table(predic.final3, predic.final5)
```

And here we can see, that the diference (on this data set) is only on prediction 
of "B" and "C" classes.    


